if (!interactive()) {
  args <- commandArgs(trailingOnly = TRUE)
  if (length(args) == 1) stop("Both input and output file are required!")
  if (length(args) == 0) {
    INPUT_FILE  <- "Iwatani_1_original.csv"
    OUTPUT_FILE <- "Iwatani_1_results_original.csv"
  } else {
    INPUT_FILE  <- args[1]
    OUTPUT_FILE <- args[2]
  }
} else {
  INPUT_FILE  <- "SocialMobility/Iwatani_1/Iwatani_1_original.csv"
  OUTPUT_FILE <- "SocialMobility/Iwatani_1/results/Iwatani_1_results_original.csv"
}

```{r, tidy}

#install.packages("devtools")
library(devtools)
#install_github("dgrtwo/broom")
library(broom)
broom::tidy(ad_aov)
```

```{r, Packages}
rm(list = ls())
Sys.setenv(LANGUAGE="en")
#source("C:/Users/siwatani/rstudio/anovakun_486.txt")
library(dplyr)
library(ggplot2)
library(ggsignif)
library(outliers)
library(reghelper)
library(gridExtra)
library(psych)
library(ltm)
library(sjPlot)
library(lme4)
library(lmerTest)
library(lavaan)
library(readr)
library(car)
library(tidyr)
library(semTools)
options(scipen=20)
```

```{r, Data and Variables}
#data_download
gen_data <- read_csv("SocialMobility/Iwatani_1/gen_data/Iwatani_1_gen_bootstrap_ind.csv")
#data <- read_csv("SocialMobility/Iwatani_1/Iwatani_1_original.csv")

#data_use <- data
data_use <- gen_data

#data_use <- INPUT_FILE

data_lw <- na.omit(data_use) 

#Age
describe(data_lw$age)
data_lw <- data_lw %>% 
  filter(age >3)
table(data_lw$age)

#Female
table(data_lw$female)

#Age
describe(data_lw$age)

#Number of participants in each condition
table(data_lw$estimation_condition)

#data_reverse
#data_reverse
data_lw <- data_lw %>% 
  mutate(low_rep_est3=7-low_rep_est3,
         low_rep_est_all=7-low_rep_est_all)

#Reputational damage estimation
data_lw<-data_lw %>% 
  mutate(low_rep_est = ( low_rep_est1+low_rep_est2+low_rep_est3
                         +low_rep_est4+low_rep_est5+low_rep_est6)/6)

#α(Reputational damage estimation)
data_estimation <- data_lw %>% filter(estimation_condition == 1)
data_alpha_estimation <- data_estimation[, c("low_rep_est1","low_rep_est2","low_rep_est3",
                                             "low_rep_est4","low_rep_est5","low_rep_est6")]
cronbach.alpha(data_alpha_estimation)
describe(data_estimation$low_rep_est)

#α(Participants’ evaluation)
data_actual <- data_lw %>% filter(estimation_condition == 0)
data_alpha_actual <- data_actual[, c("low_rep_est1","low_rep_est2","low_rep_est3",
                                     "low_rep_est4","low_rep_est5","low_rep_est6")]
cronbach.alpha(data_alpha_actual)
describe(data_actual$low_rep_est)

#addiction
data_alpha_addiction <- data_lw[, c("addiction1","addiction2","addiction3","addiction4",
                                    "addiction5","addiction6","addiction7","addiction8")]
cronbach.alpha(data_alpha_addiction)
data_lw<-data_lw %>% 
  mutate(addiction = ( addiction1+addiction2+addiction3+addiction4+
                       addiction5+addiction6+addiction7+addiction8)/8)
describe(data_lw$addiction)

#relational_mobility
data_alpha_rm <- data_lw[, c("rm1","rm2","rm3","rm4","rm5","rm6"
                             ,"rm7","rm8","rm9","rm10","rm11","rm12")]
cronbach.alpha(data_alpha_rm)
data_lw<-data_lw %>% 
  mutate(rm = ( rm1+rm2+rm3+rm4+rm5+rm6+
                rm7+rm8+rm9+rm10+rm11+rm12)/12)
describe(data_lw$rm)

#Data (female and male)
data_lw_gender_analysis <- data_lw %>% 
  filter(female<3)

#Centering
data_c <- as.data.frame(scale(data_lw))
data_c_gender_analysis <- as.data.frame(scale(data_lw_gender_analysis))

#Data(ignorer condition)
data_estimation <- data_lw %>% filter(estimation_condition == 1)
data_estimation_c <- as.data.frame(scale(data_estimation))
data_estimation_gender_analysis <- data_lw_gender_analysis %>% filter(estimation_condition == 1)
data_estimation_c_gender_analysis <- as.data.frame(scale(data_estimation_gender_analysis))
```

```{r, Hypothesis1 and 2}
mediation.model <- ' 
             # mediator
             low_rep_est ~ a*rm
             addiction ~ b*low_rep_est 
           
             # direct effect
             addiction ~  c*rm

           # indirect effect (a*b)
             ab := a*b

           # total effect
             total := c + (a*b)'

fit <- sem(mediation.model, data = data_estimation_c, meanstructure = TRUE,
           se = "boot", bootstrap = 5000)
```

```{r, Hypothesis1 and 2}

summary(fit, fit.measures=T, standardized=T, ci=TRUE)
```

```{r, Hypothesis1 and 2 Correlation}
cor1 <- cor.test(data_estimation$rm,data_estimation$low_rep_est)
cor2 <- cor.test(data_estimation$low_rep_est,data_estimation$addiction)
cor3 <- cor.test(data_estimation$rm,data_estimation$addiction)
```

```{r,Hypothesis 1 and 2 (additional)}
#adding age and gender as control variables
mediation.model2 <- ' 
             # mediator
             low_rep_est ~ a*rm
             addiction ~ b*low_rep_est 
           
             # direct effect
             addiction ~  c*rm

           # indirect effect (a*b)
             ab := a*b

           # total effect
             total := c + (a*b)

           # covariates
             addiction ~ age + female'

fit2 <- sem(mediation.model2, data = data_estimation_c_gender_analysis, meanstructure = TRUE,
           se = "boot", bootstrap = 5000)


```

```{r,Hypothesis 1 and 2 (additional)}
summary(fit2, fit.measures=T, standardized=T, ci=TRUE)
```

```{r, Hypothesis3}
resultx_1<-lm(low_rep_est ~ rm*estimation_condition,data=data_c)
summary(resultx_1)
```

```{r, Hypothesis3 (additional)}
#adding age and gender as control variables
resultx_2<-lm(low_rep_est ~ rm*estimation_condition+age+female,data=data_c_gender_analysis)
summary(resultx_2)
```

```{r,Explore}

result_reviwer1<-lm(addiction ~ rm+low_rep_est*age+female,data=data_estimation_c_gender_analysis)
summary(result_reviwer1)
```

```{r, Export File}

results <- bind_rows(
  sem1 = tidy(fit),
  sem2 = tidy(fit2),
  cor.test1 = tidy(cor1),
  cor.test2 = tidy(cor2),
  cor.test3 = tidy(cor3),
  lm1 = tidy(resultx_1),
  lm2 = tidy(resultx_2),
  lm3 = tidy(result_reviwer1),
  .id = "model"
)

#write_csv(results, "SocialMobility/Iwatani_1/results/Iwatani_1_results_original.csv")
write_csv(results, "SocialMobility/Iwatani_1/gen_data/results/Iwatani_1_results_bootstrap_ind.csv")
#write_csv(results, OUTPUT_FILE)

```